---
title: "Gun Control chi-Squared"
author: "Sandra Fogg"
date: "11/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is Sandy here, lets check out chi-squared tests!

Sandy again, can you see it?

The stars sparkle in the wilderness. 

Creator: Sandra

Read gc_df.csv data, load tidyverse, and obtaining summary counts
```{r}
# Load necessary packages
library(tidyverse)

# Load Files
gc_df <- read_csv("gc_df.csv")

# Does sex of respondent significantly affect perception of gun restrictions

# Use count function -> allows to set groupings for different categorical variables -> count how many times a #certain response occurs in the "make_get_guns" column -> Must make in contingency table format -> use a 
#function called spread -> key value in pairs -> make values (ie count) -> only want count values so we must #remove gender column (rembering female is first row)

get_guns_df <- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender)
get_guns_df

```

Collaborator for Chi-Squared. Is there a significant difference in gun control perspectives as related to access to guns for males and females?

Is there a significant association between sex and gun control recommendation?

Chi-Square
```{r}

guns_prop <-prop.table(as.matrix(get_guns_df), 1)

guns_prop

#Perform chi-square

guns_x2 <- chisq.test(get_guns_df)
guns_x2

```

Recommended govt action on gun access differs significantly for males and females ($\chi^2$(`r guns_x2$parameter`)= ..., p < 0.001)
