---
title: "Gun Control chi-Squared"
author: "Sandra Fogg"
date: "11/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is Sandy here, lets check out chi-squared tests!

Sandy again, can you see it?

The stars sparkle in the wilderness. 

Creator: Sandra

Read gc_df.csv data, load tidyverse, and obtaining summary counts
```{r}
# Load necessary packages
library(tidyverse)

# Load Files
gc_df <- read_csv("gc_df.csv")

# Does sex of respondent significantly affect perception of gun restrictions

# Use count function -> allows to set groupings for different categorical variables -> count how many times a #certain response occurs in the "make_get_guns" column -> Must make in contingency table format -> use a 
#function called spread -> key value in pairs -> make values (ie count) -> only want count values so we must #remove gender column (rembering female is first row)

get_guns_df <- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender)
get_guns_df

```

Collaborator for Chi-Squared. Is there a significant difference in gun control perspectives as related to access to guns for males and females?

Is there a significant association between sex and gun control recommendation?

Is there a significant difference between gun control perspectives, as related to access to guns, based on gender?  Is there a significant association between sex and gun control recommnedations? Is perception of gun control access independent of sex

After looking at the guns_prop - > this is a massive disparity in gun control access -> a huge gap 40-60%

If we are considering populations (one with female and one with male) - do i think that these responses are drawn from different populations

Just run chi-squared codetools

Degrees of freedom are equal to 2 -> number of columns - 1 multiplieby the number of rows - 1 

H0: There is no association between gender and gun restriction perception
HA: There is no association between gender and gun restriction perception

Recommended government action on gun access differs significantly for males and females ($\chi^2$(` r guns_x2$parameter`) = ..... p < 0.001).  Show table for actual analysis and also include table of proportions. Include notable difference for audience. Make easiest for them to understand biggest gap. GIVE VALUES of proportional differences in conclusion. 

Chi-Square
```{r}

guns_prop <-prop.table(as.matrix(get_guns_df), 1)

guns_prop

#Perform chi-square

guns_x2 <- chisq.test(get_guns_df)
guns_x2

```

Recommended govt action on gun access differs significantly for males and females ($\chi^2$(`r guns_x2$parameter`)= ..., p < 0.001)
